Appendix B: The Forecast Trap in a Sequential Decision-Making Problem

### 2022-02-28 manuscript/appendix-B.Rmd

It is worth noting that while constant escapement is used in the management of several important fish stocks such as salmon, most marine fisheries are not managed using this optimal solution for a fluctuating population, but instead rely on a 'constant harvest effort' (or constant "yield") policy.  
In the case of a deterministic model at equilibrium, these policies are identical.  Though constant-effort policies are technically sub-optimal for the problem as stated above with stochastic growth, in practice they can be more robust, such as when measurements of the current stock size $X_t$ are uncertain.  These issues are discussed in detail in @pomdp-intro.  
For our purposes, it suffices to note that constant escapement policy is relevant both from a theoretical standpoint as the optimal solution for the problem under consideration, and an applied standpoint as a policy that guides management of many salmon fisheries.The optimal control approach using SDP as illustrated here is used in a wide and growing number of conservation problems.

@@

Using the transition matrices directly, we can examine what each model would 
have forecast the future stock size to be in the following year when no fishing
occurs (note that for each model, we use the transition matrix that corresponds
to 'no fishing', `model[[state_index, ,1]]`) (Fig 2A, main text).

The transition matrices give the full (discretized) probability distribution,
from which we can easily calculate both the expected value and the 95% 
confidence interval.

>>>>

It is worth noting that while constant escapement is used in the management of several important fish stocks such as salmon, most marine fisheries are not managed using this optimal solution for a fluctuating population, but instead rely on a 'constant harvest effort' (or constant "yield") policy.
In the case of a deterministic model at equilibrium, these policies are identical. Though constant-effort policies are technically sub-optimal for the problem as stated above with stochastic growth, in practice they can be more robust, such as when measurements of the current stock size $X_t$ are uncertain. These issues are discussed in detail in @pomdp-intro.
For our purposes, it suffices to note that constant escapement policy is relevant both from a theoretical standpoint as the optimal solution for the problem under consideration, and an applied standpoint as a policy that guides management of many salmon fisheries. 
The optimal control approach using SDP as illustrated here is used in a wide and growing number of conservation problems.

@@

Using the transition matrices directly, we can examine what each model would 
have forecast the future stock size to be in the following year when no fishing
occurs (note that for each model, we use the transition matrix that corresponds
to 'no fishing', `model[[state_index, ,1]]`) (Fig 2A, main text).
The transition matrices give the full (discretized) probability distribution,
from which we can easily calculate both the expected value and the 95% 
confidence interval.
